### 2016-12-16 real/draft.tex
[draft] Fix error before suff. statistics

Which specific probability function to choose for $p(L\cond\bmtheta)$
depends, of course, on the specific simulation data. In this section,
we choose it to be the same Gamma distribution for all $L_j$,
with parameters $\bmphi = (\alpha,\beta)$,
\begin{align}
  \lleq{spc}
  p(L_j\cond \bmphi) &\sim \GammaDist(L_j\cond \alpha,\beta)
\end{align}
which has the nice property that the convolution (\ref{slm}) results
in yet another Gamma distribution,
\begin{align}
  \lleq{spd}
  \int \rmdx{\bmL}\; p(Q\cond N,\bmL)\; p(\bmL\cond N,\bmphi)
  &= \GammaDist(Q\cond N\alpha, \beta).
\end{align}
and so (\ref{gmh}) becomes in this example
\begin{align}
  \lleq{spe}
  p(Q\cond n,\bml)
  &= \sum_{N=0}^\infty \;
    p(N\cond n)\;
    \int \rmdx{\alpha}\,\rmdx{\beta}\;
    \GammaDist(Q\cond N\alpha, \beta)\;
    p(\alpha,\beta\cond n,\bml).
\end{align}
The posterior for the parameters is calculated by yet another
application of Bayes' Theorem,
\begin{align}
  \lleq{spf}
  p(\alpha,\beta\cond n,\bml)
  &= \frac{p(n,\bml\cond \alpha,\beta)\,p(\alpha,\beta)}{p(n,\bml)}
\end{align}
where the data $(n,\bml)$ must naturally follow the same
Gamma-distribution likelihood as $(N,\bmL)$, i.e.\
\begin{align}
  \lleq{spg}
  p(n,\bml\cond \alpha,\beta)
  & = \prod_{j=1}^n \GammaDist(\ell_j\cond\alpha,\beta)
    \ =\ \frac{\beta^{n\alpha} p^{\alpha-1}\,e^{-\beta q}}{[\Gamma(\alpha)]^n}
\end{align}
with compact representation of the data in terms of
$q = \sum_{j=1}^n \ell_j$ and $r = \prod_{j=1}^n \ell_j$.

The only missing piece to explicitly evaluate \refeq{spf} is the prior
$p(\alpha,\beta)$.
% To gain some insight, consider the standard $\GammaDist$ model with
% $\Kalpha = \Kbeta = 0$.
% There is a conjugate prior but
% unfortunately the normalization constant cannot be evaluated in closed
% form, so it is thus of no use for us.
% How about a noninformative prior?
The authors of \cite{moala2013bayesian} present an overview of
possible choices and conclude that the point estimate given by the
mode of the posterior is nearly insensitive to the prior choice
starting from around $n = 30$. This requirement is nearly always
satisfied and so the functional form of $p(\alpha,\beta)$ is not
important. There is, however, some explicit prior information which we
want to build into our analysis. The distribution
$p(\ell \cond \alpha, \beta)$ should always vanish at the origin,
requiring that $\alpha$ must be larger than 1.  For $\beta$, we
likewise choose a uniform prior
\begin{align}
  \lleq{sph}
  p(\alpha,\beta)
  &= \frac{1}{(\alpha_{\rm max}{-}1)\beta_{\rm max}}
  \qquad 1 < \alpha < \alpha_{\rm max},\; 0 < \beta < \beta_{\rm max}.
\end{align}
% since $\alpha_{\rm max}$ and $\beta_{\rm max}$ cancel in (\ref{spf}).
The posterior is
\begin{align}
  \lleq{spi}
  p(\alpha,\beta\cond n,\bml)
  &= \frac{1}{C}\; \frac{\beta^{n\alpha} r^{\alpha-1}\,e^{-\beta q}}{[\Gamma(\alpha)]^n}\\
  \lleq{spj}
  C &= \int_1^{\alpha_{\rm max}} d\alpha \int_0^{\beta_{\rm max}} d\beta\;
    \frac{\beta^{n\alpha} r^{\alpha-1}\,e^{-\beta q}}{[\Gamma(\alpha)]^n}
\end{align}
and hence
\begin{align}
  \lleq{spk}
  p(Q\cond n,\bml)
  &= \frac{1}{C}
    \sum_{N=0}^\infty \;
    p(N\cond n)\;
    \int \rmdx{\alpha}\,\rmdx{\beta}\;
    \GammaDist(Q\cond N\alpha, \beta)\;
    \frac{\beta^{n\alpha} p^{\alpha-1}\,e^{-\beta q}}{[\Gamma(\alpha)]^n}
\end{align}

@@

>>>>

Which specific probability function to choose for $p(L\cond\bmtheta)$
depends, of course, on the specific simulation data. In this section,
we choose it to be the same Gamma distribution for all $L_j$,
with parameters $\bmphi = (\alpha,\beta)$,
\begin{align}
  \lleq{spc}
  p(L_j\cond \bmphi) &\sim \GammaDist(L_j\cond \alpha,\beta)
\end{align}
which has the nice property that the convolution (\ref{slm}) results
in yet another Gamma distribution,
\begin{align}
  \lleq{spd}
  \int \rmdx{\bmL}\; p(Q\cond N,\bmL)\; p(\bmL\cond N,\bmphi)
  &= \GammaDist(Q\cond N\alpha, \beta).
\end{align}
and so (\ref{gmh}) becomes in this example
\begin{align}
  \lleq{spe}
  p(Q\cond n,\bml)
  &= \sum_{N=0}^\infty \;
    p(N\cond n)\;
    \int \rmdx{\alpha}\,\rmdx{\beta}\;
    \GammaDist(Q\cond N\alpha, \beta)\;
    p(\alpha,\beta\cond n,\bml).
\end{align}
The posterior for the parameters is calculated by yet another
application of Bayes' Theorem,
\begin{align}
  \lleq{spf}
  p(\alpha,\beta\cond n,\bml)
  &= \frac{p(n,\bml\cond \alpha,\beta)\,p(\alpha,\beta)}{p(n,\bml)}
\end{align}
where the data $(n,\bml)$ must naturally follow the same
Gamma likelihood as $(N,\bmL)$, i.e.\
\begin{align}
  \lleq{spg}
  p(n,\bml\cond \alpha,\beta)
  & = \prod_{j=1}^n \GammaDist(\ell_j\cond\alpha,\beta)
    \ =\ \frac{\beta^{n\alpha} r^{\alpha-1}\,e^{-\beta q}}{[\Gamma(\alpha)]^n}
\end{align}
with the data summarized by the sufficient statistics $n$,
$q \equiv \sum_{j=1}^n \ell_j$, and $r \equiv \prod_{j=1}^n \ell_j$.

The only missing piece to explicitly evaluate \refeq{spf} is the prior
$p(\alpha,\beta)$.
% To gain some insight, consider the standard $\GammaDist$ model with
% $\Kalpha = \Kbeta = 0$.
% There is a conjugate prior but
% unfortunately the normalization constant cannot be evaluated in closed
% form, so it is thus of no use for us.
% How about a noninformative prior?
The authors of \cite{moala2013bayesian} present an overview of
possible choices and conclude that the point estimate given by the
mode of the posterior is nearly insensitive to the prior choice
starting from around $n = 30$. This requirement is nearly always
satisfied and so the functional form of $p(\alpha,\beta)$ is not
important. There is, however, some explicit prior information which we
want to build into our analysis.
The distribution $p(\ell \cond \alpha, \beta)$ should always vanish at
the origin, requiring that $\alpha$ must be larger than 1.  For
$\beta$, we likewise choose a uniform prior
%
\fred{This paragraph is from the old TARDIS section. In general, we
  don't impose the constraint on $\alpha$. Only for TARDIS it seemed
  to match and prevented the fitting from running away if very few
  samples were present}
%
\begin{align}
  \lleq{sph}
  p(\alpha,\beta)
  &= \frac{1}{(\alpha_{\rm max}{-}1)\beta_{\rm max}}
  \qquad 1 < \alpha < \alpha_{\rm max},\; 0 < \beta < \beta_{\rm max}.
\end{align}
% since $\alpha_{\rm max}$ and $\beta_{\rm max}$ cancel in (\ref{spf}).
The posterior is
\begin{align}
  \lleq{spi}
  p(\alpha,\beta\cond n,\bml)
  &= \frac{1}{C}\; \frac{\beta^{n\alpha} r^{\alpha-1}\,e^{-\beta q}}{[\Gamma(\alpha)]^n}\\
  \lleq{spj}
  C &= \int_1^{\alpha_{\rm max}} d\alpha \int_0^{\beta_{\rm max}} d\beta\;
    \frac{\beta^{n\alpha} r^{\alpha-1}\,e^{-\beta q}}{[\Gamma(\alpha)]^n}
\end{align}
and hence
\begin{align}
  \lleq{spk}
  p(Q\cond n,\bml)
  &= \frac{1}{C}
    \sum_{N=0}^\infty \;
    p(N\cond n)\;
    \int \rmdx{\alpha}\,\rmdx{\beta}\;
    \GammaDist(Q\cond N\alpha, \beta)\;
    \frac{\beta^{n\alpha} p^{\alpha-1}\,e^{-\beta q}}{[\Gamma(\alpha)]^n}
\end{align}

@@

% Local Variables:
% compile-command:"rubber --pdf -W refs --synctex draft"
% End:
